---
title: "Factor analysis"
author: "Wanke Pan"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
    theme: journal
---


```{r setup, include=FALSE}
# Global chunk options
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  # dpi = 300,
  fig.width = 6,
  fig.height = 5
)

# Load necessary packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  psych,
  tidyverse,
  brms,
  tidybayes,
  ggridges,
  ggdist,
  svglite,
  patchwork,
  cmdstanr
)

# Set global ggplot theme for publication quality
theme_set(theme_minimal(base_size = 14) +
          theme(panel.grid.minor = element_blank(),
                plot.title = element_text(face = "bold"),
                axis.text = element_text(color = "black")))


# Set seed for reproducibility
set.seed(20260218)
repo_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = TRUE)
intermediate_dir <- file.path(repo_root, "results", "intermediate")
supplement_figure_dir <- file.path(repo_root, "figures", "supplement")
dir.create(supplement_figure_dir, recursive = TRUE, showWarnings = FALSE)

# Source model-fitting and visualization functions
source("fit_reliability_models.R")
source("reliability_plot_helpers.R")
```

## 1. Data Loading and Preprocessing

```{r}
# 1.1 Cross-task Data
df_cross <- read.csv(file.path(intermediate_dir, "factor_scores.csv"), check.names = FALSE)
selected_cross <- df_cross %>%
  select(subject_id, task_id, author_year, task_name,
         `Processing Efficiency`, `Decision Caution`,
         `Non-decision time`, `Inhibitory process`)

df_long <- prep_analysis_data(selected_cross)
df_long_clean <- preprocess_cognitive_data(df_long)
df_summary <- calculate_summary_stats(
  data = df_long,
  group_vars = c("author_year", "task_name", "Factor_Type"),
  value_var = "Value"
) %>%
  filter(author_year != "lee2025") %>%
  format_data_labels()

# 1.2 Temporal (Test-Retest) Data
df_retest <- read.csv(file.path(intermediate_dir, "factor_scores_retest.csv"), check.names = FALSE)
selected_retest <- df_retest %>%
  select(subject_id, session_id, task_id, author_year, task_name,
         `Processing Efficiency`, `Decision Caution`,
         `Non-decision time`, `Inhibitory process`)

df_long_retest <- prep_analysis_data(
  selected_retest,
  id_cols = c("subject_id", "session_id", "task_id", "author_year", "task_name")
)
subgroup_iccs <- calculate_subgroup_iccs(df_long_retest)
```

## 2. Modeling

```{r}
# If .rds cache exists, it loads directly; otherwise fits and saves.

# 2.1 Cross-Task Consistency Model
icc_model_fitted <- fit_icc_model(df_long_clean, cores = 4, seed = 20260218)
icc_draws <- get_posterior_icc(icc_model_fitted)
icc_draws["ICC"] <- icc_draws$ICC_conditional

# 2.2 Temporal Stability Model (Meta-Regression)
meta_model <- fit_reliability_meta_model(subgroup_iccs, cores = 4, seed = 20260218)
```

## 3. Visualization

```{r}
# Define Colors
model_colors <- c(
  "Processing Efficiency" = "#8491B4",
  "Decision Caution"      = "#3b6cb3",
  "Non-decision time"     = "#7E6148",
  "Inhibitory process"    = "#0099B4"
)

task_colors <- c(
  "Flanker" = "#b0d97c",
  "Stroop"  = "#95d8c3",
  "Simon"   = "#81cef0"
)

# Generate individual plots
p_petal_aross_task_and_lab <- plot_petal_grid(
  summary_data = df_summary,
  colors = model_colors,
  save_name = file.path(supplement_figure_dir, "factor_reliability_petal.svg")
)

p_comparison <- plot_factor_comparison(
  data = df_summary,
  colors = task_colors,
  x_tick_angle = 12
)

p_icc_ridge <- plot_icc_ridge(
  icc_data = icc_draws,
  fill_colors = model_colors,
  x_title = "Cross-tasks ICC"
)

p_diff_heatmap <- plot_diff_heatmap(icc_draws)

p_ICC_temporal <- plot_icc_forest(
  data = subgroup_iccs,
  color_palette = model_colors
)

p_temporal_Task_and_Lab <- plot_sd_comparison(meta_model)
p_temporal_difference   <- plot_sd_difference(meta_model)
```

```{r, fig.width=10, fig.height=8}
# Combine plots using patchwork
plot_top <- (p_comparison | p_icc_ridge) +
  plot_layout(widths = c(6, 4)) +
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 14, face = "bold"),
        plot.margin = margin(10, 10, 10, 10))

ggsave(file.path(supplement_figure_dir, "factor_reliability_top.svg"), plot = plot_top, device = "svg",
       width = 12, height = 5, units = "in")

plot_bottom <- (p_ICC_temporal | p_temporal_Task_and_Lab) +
  plot_layout(widths = c(7, 3)) +
  plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 14, face = "bold"),
        plot.margin = margin(10, 10, 10, 10))

ggsave(file.path(supplement_figure_dir, "factor_reliability_bottom.svg"), plot = plot_bottom, device = "svg",
       width = 12, height = 5, units = "in")

# Show combined figure
(plot_top / plot_bottom)
```
Here are the additional R Markdown chunks to extract and report specific statistical values suitable for the results section of a paper.

## Statistical Reporting

### 1. Cross-Task Consistency (ICC Estimates)

This chunk summarizes the posterior distributions of the Intra-Class Correlation coefficients derived from the first Bayesian multilevel model. It reports the Mean ICC and the 95% Credible Interval (High Density Interval) for each cognitive factor.

```{r}
# Calculate summary statistics for Cross-Task ICCs
icc_summary_stats <- icc_draws %>%
  group_by(Factor_Type) %>%
  median_qi(ICC, .width = 0.95) %>% # Calculate Median and 95% Quantile Interval
  mutate(
    Report_String = sprintf(
      "%s: Median ICC = %.2f, 95%% CI [%.2f, %.2f]",
      str_replace_all(Factor_Type, "_", " "),
      ICC,
      .lower,
      .upper
    )
  )

# Print clean output for copy-pasting
cat("--- Cross-Task Consistency Estimates ---\n")
walk(icc_summary_stats$Report_String, cat, sep = "\n")

# Optional: Return as a clean table
icc_summary_stats %>%
  select(Factor_Type, Median_ICC = ICC, Lower_95 = .lower, Upper_95 = .upper) %>%
  print()

```

### 2. Pairwise Comparisons of Consistency

This chunk quantifies the differences in consistency between factors (e.g., "Is Non-decision time significantly more consistent than Control processes?"). It calculates the mean difference and the Probability of Direction (), which represents the certainty that the difference is non-zero.

```{r}
icc_comparisons <- calculate_pairwise_stats(icc_draws)

# Print formatting
cat("--- Pairwise Differences in Consistency ---\n")
icc_comparisons %>%
  arrange(desc(abs(Mean_Difference))) %>%
  mutate(
    Report = sprintf(
      "%s: \u0394 = %.2f (pd = %.1f%%)",
      Comparison, Mean_Difference, Prob_Direction * 100
    )
  ) %>%
  pull(Report) %>%
  walk(cat, sep = "\n")

```

### 3. Temporal Stability (Test-Retest) Estimates

This chunk extracts the "average" test-retest reliability from the meta-regression model. Since the model used Fisher-Z transformation, we back-transform the results () to report them on the standard ICC scale.

```{r}
# Extract Fixed Effects (Population-Level Estimates)
temporal_fixed_effects <- meta_model %>%
  spread_draws(b_Factor_TypeControlprocess,
               b_Factor_TypeDecisionCaution,
               b_Factor_TypeInhibitoryprocess,
               b_Factor_TypeNonMdecisiontime) %>%
  pivot_longer(starts_with("b_"), names_to = "Parameter", values_to = "FisherZ_Value") %>%
  mutate(
    # Clean names
    Factor_Type = str_remove(Parameter, "b_Factor_Type"),
    # Back-transform Fisher Z to ICC
    ICC_Scale = tanh(FisherZ_Value)
  ) %>%
  group_by(Factor_Type) %>%
  median_qi(ICC_Scale, .width = 0.95)

cat("--- Estimated Temporal Stability (Test-Retest ICC) ---\n")
temporal_fixed_effects %>%
  mutate(
    Report = sprintf(
      "%s: Estimated ICC = %.2f, 95%% CI [%.2f, %.2f]",
      Factor_Type, ICC_Scale, .lower, .upper
    )
  ) %>%
  pull(Report) %>%
  walk(cat, sep = "\n")

```

### 4. Variance Decomposition (Lab vs. Task)

This chunk specifically reports the result of the "Lab vs. Task" variance comparison in the meta-regression. It quantifies how much the specific **Laboratory** (Author) contributes to variability in results compared to the specific **Task** used.

```{r}
# Extract Random Effect SDs
variance_sources <- meta_model %>%
  spread_draws(sd_author_year__Intercept, sd_task_name__Intercept) %>%
  mutate(
    diff_sd = sd_author_year__Intercept - sd_task_name__Intercept,
    ratio = sd_author_year__Intercept / sd_task_name__Intercept
  )

# Calculate stats
lab_sd_mean <- mean(variance_sources$sd_author_year__Intercept)
task_sd_mean <- mean(variance_sources$sd_task_name__Intercept)
prob_lab_greater <- mean(variance_sources$diff_sd > 0)

cat("--- Sources of Heterogeneity in Reliability ---\n")
cat(sprintf("Posterior Mean SD (Lab/Author): %.3f\n", lab_sd_mean))
cat(sprintf("Posterior Mean SD (Task):       %.3f\n", task_sd_mean))
cat(sprintf("Probability that Lab variability > Task variability: %.1f%%\n", prob_lab_greater * 100))

# Bayes Factor estimate (Savage-Dickey density ratio approximation logic)
# Note: simple ratio of posteriors here
cat(sprintf("On average, Lab heterogeneity is %.2fx larger than Task heterogeneity.\n",
            mean(variance_sources$ratio)))

```
### 5. Task-Specific Temporal Stability Estimates & Comparisons

```{r}
# 1. Fit the task-specific meta-regression with fit_task_fixed_meta_model().
# The fitted model is cached under results/intermediate/.
task_meta_model <- fit_task_fixed_meta_model(
  subgroup_iccs,
  cores = 4,
  seed = 20260218
)
```

```{r}
# 2. Extract Task Estimates and Back-Transform to ICC scale
task_draws <- task_meta_model %>%
  spread_draws(`b_task_name.*`, regex = TRUE) %>%
  pivot_longer(starts_with("b_task_name"), names_to = "Task", values_to = "FisherZ_Value") %>%
  mutate(
    Task = str_remove(Task, "b_task_name"),
    ICC_Scale = tanh(FisherZ_Value) # Back-transform Fisher Z to standard ICC
  )

# 3. Summarize Task Estimates & Test against 0
task_summary <- task_draws %>%
  group_by(Task) %>%
  summarise(
    Median_ICC = median(ICC_Scale),
    Lower_95 = quantile(ICC_Scale, 0.025),
    Upper_95 = quantile(ICC_Scale, 0.975),
    # Probability of Direction: What % of the posterior is > 0?
    Prob_Greater_Zero = mean(ICC_Scale > 0)
  ) %>%
  mutate(
    Report = sprintf(
      "%s: Median ICC = %.2f, 95%% CI [%.2f, %.2f], P(ICC > 0) = %.1f%%",
      str_to_title(Task), Median_ICC, Lower_95, Upper_95, Prob_Greater_Zero * 100
    )
  )

walk(task_summary$Report, cat, sep = "\n")
```

```{r}

# 4. Pairwise Comparisons Between Tasks
tasks <- unique(task_draws$Task)
task_combs <- combn(tasks, 2, simplify = FALSE)

task_comparisons <- map_df(task_combs, function(pair) {
  t1 <- pair[1]
  t2 <- pair[2]

  # Extract posterior distributions for both tasks
  p1 <- task_draws %>% filter(Task == t1) %>% pull(ICC_Scale)
  p2 <- task_draws %>% filter(Task == t2) %>% pull(ICC_Scale)

  # Calculate difference distribution
  diff_dist <- p1 - p2
  mean_diff <- mean(diff_dist)

  # Probability of Direction for the difference
  prob_dir <- max(mean(diff_dist > 0), mean(diff_dist < 0))

  tibble(
    Comparison = paste0(str_to_title(t1), " vs ", str_to_title(t2)),
    Diff_Mean = mean_diff,
    Lower_95 = quantile(diff_dist, 0.025),
    Upper_95 = quantile(diff_dist, 0.975),
    Prob_Direction = prob_dir
  )
})

# Print formatted comparisons sorted by largest effect
task_comparisons %>%
  arrange(desc(abs(Diff_Mean))) %>%
  mutate(
    Report = sprintf(
      "%s: \u0394 ICC = %+.2f, 95%% CI [%+.2f, %+.2f] (pd = %.1f%%)",
      Comparison, Diff_Mean, Lower_95, Upper_95, Prob_Direction * 100
    )
  ) %>%
  pull(Report) %>%
  walk(cat, sep = "\n")
```

```{r}
# 5. Visualize Task Posteriors and Pairwise Differences
# Requires: library(ggplot2), library(ggdist), library(patchwork)

# 5.1 Prepare data for difference distributions
diff_draws <- map_df(task_combs, function(pair) {
  t1 <- pair[1]
  t2 <- pair[2]

  p1 <- task_draws %>% filter(Task == t1) %>% pull(ICC_Scale)
  p2 <- task_draws %>% filter(Task == t2) %>% pull(ICC_Scale)

  # Calculate full posterior difference for ggdist
  tibble(
    Comparison = paste0(str_to_title(t1), " - ", str_to_title(t2)),
    Diff = p1 - p2
  )
})

# 5.2 Plot A: Posterior Distributions of Individual Tasks
library(ggplot2)
library(ggdist)
library(patchwork)

p_tasks <- task_draws %>%
  mutate(Task = str_to_title(Task)) %>%
  ggplot(aes(x = ICC_Scale, y = Task, fill = Task)) +
  # stat_halfeye automatically plots the density, point estimate, and interval
  stat_halfeye(
    alpha = 0.7,
    .width = 0.95,
    point_interval = median_hdi, # Use Highest Density Interval (HDI)
    justification = -0.1,        # Shift density slightly up
    height = 0.6
  ) +
  scale_fill_viridis_d(guide = "none") +
  labs(
    title = "A. Task-Specific Posterior Distributions",
    x = "ICC Estimate",
    y = "Task"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.y = element_text(face = "bold")
  )

# 5.3 Plot B: Posterior Distributions of Pairwise Differences
p_diffs <- diff_draws %>%
  ggplot(aes(x = Diff, y = Comparison, fill = Comparison)) +
  stat_halfeye(
    alpha = 0.7,
    .width = 0.95,
    point_interval = median_hdi, # Calculate and show 95% HDI
    justification = -0.1,
    height = 0.6
  ) +
  # Add a reference line at 0 (No difference)
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 1) +
  scale_fill_viridis_d(option = "magma", guide = "none") +
  labs(
    title = "B. Pairwise Differences (\u0394 ICC) with 95% HDI",
    x = "Difference in ICC (\u0394)",
    y = "Comparison"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.y = element_text(face = "bold")
  )

# 5.4 Combine plots using patchwork
combined_plot <- p_tasks / p_diffs +
  plot_layout(heights = c(1, 1))

ggsave(file.path(supplement_figure_dir, "factor_reliability_cross_task.svg"), combined_plot, device = svglite, width = 7, height = 7)

# Display the plot
combined_plot
```




