---
title: "Cognitive Model Parameter EFA: 4-Factor Solution"
author: "Wanke Pan"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: yes
    toc_depth: 3
    toc_float: yes
    theme: journal
---

```{r setup, include=FALSE}
# Global chunk options
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  # dpi = 300,
  fig.width = 6,
  fig.height = 5
)

# Load necessary packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  psych,      # Main package for Factor Analysis
  pheatmap,   # For sophisticated heatmaps
  dplyr,      # Data manipulation
  ggplot2,    # General plotting
  corrplot,   # Correlation visualization
  tidyr,      # Data reshaping
  stringr,    # String manipulation
  latex2exp,
  GPArotation # Required for specific rotations
)

# Set seed for reproducibility
set.seed(20260120)

repo_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = TRUE)
intermediate_dir <- file.path(repo_root, "results", "intermediate")
dir.create(intermediate_dir, recursive = TRUE, showWarnings = FALSE)

```

# 1. Data Preparation

## 1.1 Load and Clean Data Names

We load the data and immediately clean the column names. The original file contains LaTeX formatting (e.g., ) which makes plotting difficult. We replace these with readable text.

```{r}
# Read data
# Note: Ensure the path is correct relative to your working directory
raw_data <- read.csv(file.path(intermediate_dir, "subject_indices.csv"), check.names = FALSE)

# Select relevant columns (excluding indices 24-28 as per original script)
df_analysis <- raw_data %>%
  select(-c(24:28))
```

## 1.2 Data Preprocessing (Standardization)

Since parameters (like  vs ) have vastly different scales, we must standardize the data.

```{r}
# Optional: Filter for a specific task if needed
# df_analysis <- df_analysis %>% filter(task_id == "eisenberg2019flanker")

# Remove non-numeric columns (task_id, subject indices)
df_numeric <- df_analysis %>%
  select(-task_id, -subject_id) %>%
  select_if(is.numeric)

# Standardize data (Z-score) to ensure equal weight in EFA
df_scaled <- scale(df_numeric)

cat("Data dimensions for EFA:", nrow(df_scaled), "observations x", ncol(df_scaled), "variables.\n")

```

# 2. Determining Number of Factors

Before running the final model, we perform a **Parallel Analysis** and inspect the **Scree Plot**.

* **Scree Plot:** Displays the eigenvalues (variance explained) for each factor. We look for the "elbow" where the drop levels off.
* **Parallel Analysis:** Compares the actual data eigenvalues to those generated from random noise. We should retain factors where `Actual Data > Simulated Data`.

```{r}
# Parallel Analysis and Scree Plot
psych::fa.parallel(
  df_scaled,
  fm = "ml",       # Maximum Likelihood
  fa = "fa",       # Show Factor Analysis results (not PCA)
  n.iter = 50,     # Number of simulated iterations
  main = "Scree Plot & Parallel Analysis"
)

```

> **Interpretation:** Look at the blue line (Actual Data). If the blue line stays above the red dotted line (Resampled Data) for the first 4 points, a 4-factor solution is statistically justified.

# 3. Exploratory Factor Analysis (4 Factors)

We perform EFA extracting exactly **4 factors** based on the hypothesis/scree results.

* **Extraction:** `ml` (Maximum Likelihood).
* **Rotation:** `oblimin`. We use oblique rotation because cognitive processes (Inhibition, Speed, etc.) are expected to correlate in nature.

```{r}
# Define number of factors
N_FACTORS <- 4

# Run Factor Analysis (Oblique Rotation)
efa_fit <- psych::fa(
  r = df_scaled,
  nfactors = N_FACTORS,
  rotate = "oblimin",  # Allows correlations between factors
  # n.iter = 1000,       # For bootstrape
  fm = "ml"            # Maximum Likelihood
)

# Print basic model fit
print(efa_fit$fit)
cat("\nTotal Variance Explained:", round(sum(efa_fit$Vaccounted["Proportion Var",]), 3) * 100, "%\n")
```


```{r}
# --- Apply Custom Labels ---
# CAUTION: Ensure these labels match the statistical output order (Factor 1, 2, 3, 4).
# Check the 'Proportion Var' in the summary to see which factor explains most variance.
latent_labels <- c("Processing Efficiency", "Decision Caution", "Non-decision time", "Inhibitory process")

# Rename columns in Loadings and Correlation Matrix
colnames(efa_fit$loadings) <- latent_labels
colnames(efa_fit$Phi) <- rownames(efa_fit$Phi) <- latent_labels
```



## 3.1 Interpretation of Loadings

We inspect which variables load onto which factors. We suppress small loadings (< 0.4) for clarity.

```{r}
# Print sorted loadings with new names
print(psych::fa.sort(efa_fit$loadings), cutoff = 0.45)

```

## 3.2 Visualization of Loadings


```{r fig.height=5, fig.width=10}
latex_labels <- rownames(efa_fit$loadings) %>%
    sapply(function(x) {
      tryCatch(
        latex2exp::TeX(x),
        error = function(e) x
      )
    })

loadings_mat <- unclass(efa_fit$loadings)
heatmap_data <- t(loadings_mat)
# 4. Create the Heatmap
pheatmap::pheatmap(
  heatmap_data,
  scale = "none",          # Loadings are already on -1 to 1 scale, usually don't scale rows/cols further
  cluster_rows = FALSE,    # Keep our named Factors (Control, Caution...) ordered
  cluster_cols = TRUE,     # Cluster parameters to group similar ones together
  clustering_distance_cols = "correlation",
  labels_col = latex_labels, # Apply the LaTeX labels
  display_numbers = TRUE,  # Show the correlation numbers
  number_format = "%.2f",  # 2 decimal places
  fontsize_number = 8,
  fontsize_col = 10,       # Adjust font size for LaTeX labels
  main = "Factor Loadings (Oblique Rotation)",
  treeheight_col = 20      # Height of the dendrogram
)
```


# 4. Factor Score Correlations

Since we used oblique rotation (`oblimin`), the latent factors are allowed to correlate. The table below shows how the 4 extracted mechanisms relate to each other.

```{r}
# Get factor correlations (Phi matrix) - Names are already applied in Section 3
phi_matrix <- efa_fit$Phi

corrplot::corrplot(
  phi_matrix,
  method = "color",       # Use color intensity
  addCoef.col = "black",  # Add number in black
  type = "lower",         # Show lower triangle
  tl.col = "black",       # Text label color
  tl.srt = 45,            # Rotate text labels
  title = "Correlations among Latent Factors",
  mar = c(0,0,2,0)
)

```

# 5. Report Results

```{r}
# FACTOR ANALYSIS REPORTING SCRIPT

# 1. Prepare Data for Reporting
# Extract loadings and variance tables
factor_loadings <- unclass(efa_fit$loadings)
variance_accounted <- efa_fit$Vaccounted

report_labels <- rownames(factor_loadings)

# 2. Diagnostics (KMO & Bartlett)
cat("\n=============================================\n")
cat("      FACTOR ANALYSIS DIAGNOSTICS REPORT     \n")
cat("=============================================\n\n")

# KMO test
kmo_result <- psych::KMO(df_scaled)
cat("--- Kaiser-Meyer-Olkin (KMO) Measure ---\n")
cat("Overall MSA:        ", round(kmo_result$MSA, 3), "\n")
cat("Interpretation:     ",
    ifelse(kmo_result$MSA >= 0.8, "Excellent",
    ifelse(kmo_result$MSA >= 0.7, "Good",
    ifelse(kmo_result$MSA >= 0.6, "Mediocre",
    ifelse(kmo_result$MSA >= 0.5, "Poor", "Unacceptable")))), "\n\n")

# Bartlett's test
bartlett_result <- psych::cortest.bartlett(df_scaled)
cat("--- Bartlett's Test of Sphericity ---\n")
cat("Chi-square:         ", round(bartlett_result$chisq, 2), "\n")
cat("p-value:            ", format(bartlett_result$p.value, scientific = TRUE), "\n")
cat("Significance:       ", ifelse(bartlett_result$p.value < 0.05,
                              "Significant (Data suitable for FA)",
                              "Not significant (Data may be unsuitable)"), "\n\n")

# 3. Factor Correlations (Crucial for Oblimin)
cat("=============================================\n")
cat("      FACTOR CORRELATIONS (PHI MATRIX)       \n")
cat("=============================================\n")

if (!is.null(efa_fit$Phi)) {
  cat("Note: Since 'oblimin' rotation was used, factors are allowed to correlate.\n")
  cat("Moderate correlations (0.3 - 0.5) justify the use of oblique rotation.\n\n")

  # Print the Phi matrix rounded
  print(round(efa_fit$Phi, 3))

  cat("\nCheck:\n")
  cat(" * High correlations (> 0.80): Factors may be redundant (multicollinearity).\n")
  cat(" * Very low correlations (< 0.10): Factors are essentially orthogonal.\n\n")
} else {
  cat("Phi matrix is NULL. The rotation method might be orthogonal (e.g., Varimax).\n\n")
}

# 4. Factor Interpretation (Loadings)
cat("=============================================\n")
cat("      FACTOR INTERPRETATION & LOADINGS       \n")
cat("=============================================\n")

cat("Variance explained by factors:\n")
print(round(variance_accounted[2, ], 3))
cat("Cumulative variance explained:", round(sum(variance_accounted[2, ]), 3), "\n\n")


for (i in 1:ncol(factor_loadings)) {
  factor_name <- colnames(factor_loadings)[i]

  # Identify row index for "Proportion Var" (usually 2nd row in Vaccounted)
  prop_var_row <- which(rownames(variance_accounted) == "Proportion Var")
  if(length(prop_var_row) == 0) prop_var_row <- 2 # Fallback

  # Get loadings for this factor
  current_loadings <- factor_loadings[, i]
  names(current_loadings) <- report_labels # Apply the latex/clean labels

  # Filter for high loadings (> 0.4 or < -0.4)
  high_loadings_idx <- abs(current_loadings) > 0.4
  sorted_loadings <- sort(current_loadings[high_loadings_idx], decreasing = TRUE, index.return = FALSE)

  # Print Header
  cat(sprintf(">> Factor: %s\n", factor_name))
  cat(sprintf("   Variance Explained: %.1f%%\n", variance_accounted[prop_var_row, i] * 100))

  # Print Variables
  if (length(sorted_loadings) > 0) {
    cat("   Top Items:\n")
    for (j in 1:length(sorted_loadings)) {
      var_name <- names(sorted_loadings)[j]
      loading <- sorted_loadings[j]
      cat(sprintf("   %-40s : %+.3f\n", var_name, loading))
    }
  } else {
    cat("   No high loadings (> 0.4) found for this factor.\n")
  }
  cat("\n")
}
```

```{r}
# 6. Extract Factor Scores & Merge

subj_scores <- data.frame(efa_fit$scores)
colnames(subj_scores) <- latent_labels


if(nrow(raw_data) == nrow(subj_scores)) {
  final_data <- cbind(raw_data, subj_scores)
  cat("Success! Merged scores. New dimensions:", nrow(final_data), "rows x", ncol(final_data), "columns.\n")
} else {
  stop("Error: Row mismatch. The number of rows in raw_data does not match the factor scores.")
}

output_filename <- file.path(intermediate_dir, "factor_scores.csv")

write.csv(final_data, output_filename, row.names = FALSE)
```


## For retest datasets

```{r}
raw_data_retest <- read.csv(file.path(intermediate_dir, "subject_indices_retest.csv"), check.names = FALSE)

df_numeric_retest <- raw_data_retest %>%
  select(-c(24:28)) %>%
  select(-task_id, -subject_id, -session_id) %>%
  select_if(is.numeric)

df_scaled_retest <- scale(df_numeric_retest)

N_FACTORS <- 4
efa_fit_retest <- psych::fa(
  r = df_scaled_retest,
  nfactors = N_FACTORS,
  rotate = "oblimin",  # Allows correlations between factors
  # n.iter = 1000,       # For bootstrape
  fm = "ml"            # Maximum Likelihood
)

latent_labels <- c("Processing Efficiency", "Decision Caution", "Non-decision time", "Inhibitory process")
colnames(efa_fit_retest$loadings) <- latent_labels
colnames(efa_fit_retest$Phi) <- rownames(efa_fit_retest$Phi) <- latent_labels

# print(psych::fa.sort(efa_fit$loadings), cutoff = 0.45)
subj_scores_retest <- data.frame(efa_fit_retest$scores)
colnames(subj_scores_retest) <- latent_labels

if(nrow(raw_data_retest) == nrow(subj_scores_retest)) {
  final_data_retest <- cbind(raw_data_retest, subj_scores_retest)
  cat("Success! Merged scores. New dimensions:", nrow(final_data_retest), "rows x", ncol(final_data_retest), "columns.\n")
} else {
  stop("Error: Row mismatch. The number of rows in raw_data does not match the factor scores.")
}
output_filename_retest <- file.path(intermediate_dir, "factor_scores_retest.csv")
write.csv(final_data_retest, output_filename_retest, row.names = FALSE)
```

